---
title: "Homework 5"
author: "Alison Barbee"
date: "2022-11-30"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE)
```


```{r data}
library(readr)

homicide_data <- read_csv("data/homicide-data.csv")
```

#Pick one city in the data. 

```{r Los Angeles}
library(tidyverse)

losAngeles <- homicide_data %>%
  mutate(city_name = str_c(homicide_data$city, homicide_data$state, sep = ", ")) %>%
  filter(city_name == "Los Angeles, CA") %>%
  rename()

```

#Mapping it out

Create a map showing the locations of the homicides in that city, using the sf framework discussed in class.
 
Use tigris to download boundaries for some sub-city geography (e.g., tracts, block groups, county subdivisions) to show as a layer underneath the points showing homicides. 


I used tigris to set county boundaries within California to represent the different subdivisions within the state. 

```{r Map, tigris_use_cache = TRUE}
library(sf)
library(tigris)
library(ggplot2)
library(viridis)
library(MAP)

ca_counties <- counties(state = "CA", cb = TRUE, class = "sf")

ggplot() + 
  geom_sf(data = ca_counties, color = "lightgray")

```


```{r}
ca_homicides <- losAngeles %>% 
  select(uid, reported_date, victim_race, lat, lon, disposition)

ca_homicides <- st_as_sf(ca_homicides, coords = c("lon", "lat")) %>%
  st_set_crs(4269)

```

Use different facets for solved versus unsolved homicides 
Use different colors to show the three race groups with the highest number of homicides for that city 
(you may find the fct_lump function from forcats useful for this).

```{r}

ggplot() +
  geom_sf(data = ca_counties, color = "lightgray", fill = "gray") +
  xlim(c(-118.8, -118)) + ylim(c(33.7, 34.35)) +
  geom_sf(data = ca_homicides, mapping = aes(color = victim_race,
                                             shape = disposition,
                                             stat = "sf")) +
  ggtitle("Location of homicides in Los Angeles")
    
map + facet_wrap(vars(status))
```

```{r}

```